---
title: "Lab 6 Github and Iteration"
author: "Jasmin Cabarios"
date: "7/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
library(purrr)
<<<<<<< HEAD
library(dplyr)
=======
>>>>>>> 7e8bdb54c674184c7379366196bba9a2647e5442
xmas <- read.csv("https://www.dropbox.com/s/e584pryn8evm1gz/xmas.csv?dl=1")

```

# Step One

Note that the gifts are listed in singular: for example, on day 5 the narrator receives “5 golden rings”, but the entry in the dataset for the gift on day 5 simply says “ring”.
In your twelvedays package, navigate to the file pluralize_gift.R in the R folder. You will find some incomplete code for a function called pluralize_gift that takes a gift and returns the appropriate plural.
Complete this function code.

```{r}

pluralize_gift <- function(gift){
  newgift <- gift

  newgift <- newgift%>%
    str_replace("oo", "ee") %>%
    str_replace("y$", "ies") %>%
    str_replace(newgift, glue("{newgift}s") ) %>%
    str_replace("partridges", "partridge")
    
  
  
}

xmas <- xmas %>%
  mutate(Gift.Item = (map_chr(xmas$Gift.Item, pluralize_gift)))
```

# Step 2

Write a function called make_phrase that takes as input the necessary information, and returns a phrase.
should return:

"ten lords a-leaping"

Try your function out on the xmas data, by making a new variable containing the daily phrases.



```{r}

xmas <- xmas %>%
  mutate(num_word = c("one", "two", "three", "four", 
                      "five", "six", "seven", "eight", 
                      "nine", "ten", "eleven", "twelve"))

make_phrase <- function(num, num_word, item, verb = " ", adjective = " ", location = " ", nums) {

  verb <- str_replace_na(verb, "")
  adjective <- str_replace_na(adjective, "")
  location <- str_replace_na(location, "")
 
  return(trimws(gsub("\\s+", " ", glue("{nums} {adjective} {item} {verb} {location}"))))
}


make_phrase(num = 10, 
            num_word = "ten", 
            item = "lords", 
            verb = "a-leaping", 
            adjective = "", 
            location = "",
            nums = "ten")
make_phrase(num = 2, 
            num_word = "two", 
            item = "doves", 
            verb = "", 
            adjective = "turtle", 
            location = "",
            nums = "two")




<<<<<<< HEAD
xmas <- xmas %>%
=======
xmas %>%
>>>>>>> 7e8bdb54c674184c7379366196bba9a2647e5442
  mutate(
    Full.Phrase = pmap_chr(list(Day, Day.in.Words, Gift.Item, Verb, 
                                Adjective, Location, num_word), make_phrase)
  )
<<<<<<< HEAD

print(xmas$Full.Phrase)

=======
>>>>>>> 7e8bdb54c674184c7379366196bba9a2647e5442
```


# Step Three
Write a function called sing_line that takes as input:
A dataset
A number indicating which day to sing about
The name of a column in the dataset that contains the phrases for each day.


```{r}
<<<<<<< HEAD
sing_day <- function(dataset, days, line, phrase_col){

  phrases <- dataset %>% pull({{phrase_col}})
  days <- dataset %>% pull({{days}})
  day <- days[line]
  
  
  phrases <- phrases[line:1]
  new.phrase <- glue_collapse(map(phrases, paste), sep = "\n")
 
  song <- glue("On the {day} day of Christmas, my true love sent to me,
               {new.phrase}.")
  
  
  return(song)
  
}

sing_day(xmas, Day.in.Words, 12, Full.Phrase)
=======
sing_day <- function(dataset, line, phrase_col){

  phrases <- dataset %>% pull({{phrase_col}})
  day <- dataset$Day.in.Words[line]
  print(day)
  
  
  
  
  
}

>>>>>>> 7e8bdb54c674184c7379366196bba9a2647e5442

```


